SMT-Based Context-Bounded Model Checking for Embedded Systems: Challenges and Future Trends

### 2016-03-26 paper.tex
corrections to section 3

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints), use assertion-based verification, and high-level processor models during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure2.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness; additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions; and
	\item legacy designs.%, which are usually developed with low-level languages.
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices.

>>>>

State-of-the-art verification methodologies for embedded systems generate test vectors (with constraints) and use assertion-based verification and high-level processor models, during simulation~\cite{Behrend15,Lettnin09}, as shown in Figure~\ref{verification-methodologies}. 
%
\begin{figure}[h]
	\centering
	\includegraphics[scale=0.35]{figure2.eps}
	\caption{Verification methodologies for embedded systems.}
	\label{verification-methodologies}
\end{figure}

In particular, the main challenges regarding the verification of embedded systems lie on improving coverage, where more system functions are verified, reducing verification time, {\it i.e.}, pruning the state-space exploration during verification, and incorporating system models, which allow specific checks regarding system behavior and not only code correctness. Additionally, embedded system verification raises additional challenges, such as 
%
\begin{enumerate}
	\item time and energy constraints;
	\item handling of concurrent software;
	\item platform restrictions;
	\item legacy designs; and %, which are usually developed with low-level languages.
	\item \textcolor{blue}{support to different languages and interfaces};
\end{enumerate}

Indeed, the first two aspects are of extreme relevance in micro-grids and cyber-physical systems, in order to ensure reliability, which is a key issue for (smart) cities, industries, and consumers, and the third one is essential in systems that implement device models, such as digital filters and controllers, which present a behavior that is highly dependent on signal inputs and outputs and whose deployment may be heavily affected by hardware restrictions. The fourth aspect is inherent to a large number of embedded systems from  telecommunications, control systems, and medical devices. \textcolor{blue}{Finally, the last one is related to the evolution of development processes and technologies, which may delay the application of suitable verification approaches.}
